Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-07-21 paperDraft.tex
start of assurance test section

\subsection{Assurance Test Planning}
Assurance Testing
consumer and producer risk

\subsubsection{Traditional Approach}
no producer risk

@@

>>>>

\subsection{Assurance Test Planning}
For all statisticical test planning we are interested in minimizing error rates
while using the resoruces avalible as efficently as possible.  In the DoD
acquisition process the error rates will be refrenced in terms of risk.
Consumer risk being the probability of a unacceptable product passing a given
test.  Producer risk being the probability of an acceptable product failing a
given test.

\subsubsection{Traditional Approach}
Traditional methods do not use any past data for determining the testing
proceedure.  The only rely on distributional assumptions and asymptoic results.

@@

With Bayesian statistical approach we can incorperate the supplementary data
from previous testing phases with the hopes of minimizing the resorces needed
for testing.
